\thetitle

### 2022-06-28 thesis/paper.tex
typo

\ifen
Because $\Delta_j(v)$ is rounded down in the recursion relation defined by \eqref{recursionrelationforcostmindp} and \eqref{deltajvdef}, if $j \in \mathcal{W}[j, v]$, then the true value of $(1 - f_j) v\bigl(\mathcal{W}[j-1, v- \Delta_j(v)]\bigr) + f_j t_j$ may exceed the fixed-point valuation $v$ of $\mathcal{W}[j, v]$, but not by more than $10^{-P}$. This error accumulates additively with each school added to $\mathcal{W}$, but the number of additions is at most $m$. Therefore, where $v'(\mathcal{W})$ denotes the fixed-point valuation of $\mathcal{W}$ recorded in line \ref{vrecordedhere} of the algorithm, 
$v(\mathcal{W}) - v'(\mathcal{W}) \leq m 10^{-P}$.
\else
\eqref{recursionrelationforcostmindp}과(와) \eqref{deltajvdef}(으)로 정의된 점화식에 따라 $\Delta_j(v)$를 내림하기 때문에, $j \in \mathcal{W}[j, v]$이면 $(1 - f_j) v\bigl(\mathcal{W}[j-1, v- \Delta_j(v)]\bigr) + f_j t_j$의 실제값은 $\mathcal{W}[j, v]$의 고정소숫점 가치인 $v$보다 클 수 있는데 최대한 $10^{-P}$ 만큼의 차이가 발생한다. 또한 이 오차는 $\mathcal{W}$에 학교를 추가할 때마다 가산적으로 누적되는데 추가하는 학교의 개수는 최대한 $m$이다. 따라서 알고리즘의 \ref{vrecordedhere}줄에서 기록하는 $\mathcal{W}$의 고정소숫점 가치가 $v'(\mathcal{W})$일 때, $v(\mathcal{W}) - v'(\mathcal{W}) \leq m 10^{-P}$이 성립한다.
\fi

>>>>

\ifen
Because $\Delta_j(v)$ is rounded down in the recursion relation defined by \eqref{recursionrelationforcostmindp} and \eqref{deltajvdef}, if $j \in \mathcal{W}[j, v]$, the true value of $(1 - f_j) v\bigl(\mathcal{W}[j-1, v- \Delta_j(v)]\bigr) + f_j t_j$ may exceed the fixed-point valuation $v$ of $\mathcal{W}[j, v]$, but not by more than $10^{-P}$. This error accumulates additively with each school added to $\mathcal{W}$, but the number of additions is at most $m$. Therefore, where $v'(\mathcal{W})$ denotes the fixed-point valuation of $\mathcal{W}$ recorded in line \ref{vrecordedhere} of the algorithm, 
$v(\mathcal{W}) - v'(\mathcal{W}) \leq m 10^{-P}$.
\else
\eqref{recursionrelationforcostmindp}과(와) \eqref{deltajvdef}(으)로 정의된 점화식에 따라 $\Delta_j(v)$를 내림하기 때문에, $j \in \mathcal{W}[j, v]$이면 $(1 - f_j) v\bigl(\mathcal{W}[j-1, v- \Delta_j(v)]\bigr) + f_j t_j$의 실제값은 $\mathcal{W}[j, v]$의 고정소숫점 가치인 $v$보다 클 수 있는데 최대한 $10^{-P}$ 만큼의 차이가 발생한다. 또한 이 오차는 $\mathcal{W}$에 학교를 추가할 때마다 가산적으로 누적되는데 추가하는 학교의 개수는 최대한 $m$이다. 따라서 알고리즘의 \ref{vrecordedhere}줄에서 기록하는 $\mathcal{W}$의 고정소숫점 가치가 $v'(\mathcal{W})$일 때, $v(\mathcal{W}) - v'(\mathcal{W}) \leq m 10^{-P}$이 성립한다.
\fi
